Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-08-22 Multiresolution_framework/ltx/manuscript.tex
minor edits

\author[TNG]{P. Aram\corref{cor1}}
\ead{parham.aram@univ-amu.fr}
\author[DEEE,BI]{D. R. Freestone}
\ead{deanrf@unimelb.edu.au} 
\author[CU]{M. Dewar}
\ead{md@bit.ly}
\author[UM]{K. Scerri}
\ead{kenneth.scerri@um.edu.mt} 
 \author[TNG]{V. Jirsa}
\ead{viktor.jirsa@univ-amu.fr}
\author[DEEE,BI]{D. B. Grayden}
\ead{grayden@unimelb.edu.au}
\author[US]{V. Kadirkamanathan}
\ead{visakan@sheffield.ac.uk}

@@

	$\mathbb{R}$&\parham{The set of all real numbers}&n.a.\\
	$\mathbb{Z}$&\parham{The set of all integers}&n.a.\\

@@

\parham{To calculate the frequency response of the B-spline wavelet the Fourier transform of $N_1(r)$ is first calculated, 

@@

\end{align} }

>>>>

\author[TNG,US]{P. Aram\corref{cor1}}
\ead{parham.aram@univ-amu.fr}
\author[DEEE,BI]{D. R. Freestone}
\ead{deanrf@unimelb.edu.au} 
\author[CU]{M. Dewar}
\ead{md@bit.ly}
\author[UM]{K. Scerri}
\ead{kenneth.scerri@um.edu.mt} 
 \author[TNG]{V. Jirsa}
\ead{viktor.jirsa@univ-amu.fr}
\author[DEEE,BI]{D. B. Grayden}
\ead{grayden@unimelb.edu.au}
\author[US]{V. Kadirkamanathan}
\ead{visakan@sheffield.ac.uk}

@@

	$\mathbb{R}$&The set of all real numbers&n.a.\\
	$\mathbb{Z}$&The set of all integers&n.a.\\

@@

To calculate the frequency response of the B-spline wavelet the Fourier transform of $N_1(r)$ is first calculated, 

@@
